This script is to make plots for the manuscript. It is adapted from `plots_for_poster.Rmd`.

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Users/nadeaus/Documents/Repos/wastewaterr')
remake_map <- F
```

Load packages
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(xlsx)
library(cowplot)
library(RColorBrewer)
library(scales)

# Spatial packages
if (remake_map) {
  library(rgdal)     # for reading and writing data, note how it also loads "sp" package
  library(rgeos)     # for reading and writing data
  library(tmap)      # for visualization and plotting
  library(tmaptools) # for visualization and plotting
}
```

Specify colors and theme elements
```{r}
influenza_type_colors <- brewer.pal(n = 8, name = "Set2")[c(1, 2, 5)]
names(influenza_type_colors) <- c("IBV", "IAV", "ILI")
influenza_type_color_scale <- scale_color_manual(values = influenza_type_colors, aesthetics = c("color", "fill"))

catchment_area_colors <- brewer.pal(n = 8, name = "Set2")[c(4, 6, 3)]
background_plot_color <- brewer.pal(n = 8, name = "Set2")[7]

data_type_colors <- brewer.pal(n = 8, name = "Set1")[1:2]
names(data_type_colors) <- c("Cases", "Wastewater")
data_type_color_scale <- scale_color_manual(name = element_blank(), values = data_type_colors, aesthetics = c("color", "fill"))

delay_dist_colors <- brewer.pal(n = 8, name = "Set1")[c(2, 8)]
names(delay_dist_colors) <- c("Fecal", "Respiratory")
delay_dist_color_scale <- scale_color_manual(name = element_blank(), values = delay_dist_colors, aesthetics = c("color", "fill"))

shared_theme <- theme_bw()
shared_date_scale <- scale_x_date(date_breaks = "1 month", date_labels = "%b %y", expand = c(0, 0))
shared_date_scale_coarse <- scale_x_date(date_breaks = "1 month", date_labels = "%b\n%y", expand = c(0, 0))

catchment_factor_levels <- c("Zurich", "Geneva", "Basel")

line_size <- 1
```

Load data
```{r}
# Re estimates
# suffix <- "_fecal_sld_22-10-26_clean_data"
# suffix_resp_dist <- "_resp_sld_22-10-26_clean_data"
# ww_re <- read.csv(paste0("results/ww_re_estimates", suffix, ".csv"))
# ww_re_resp_dist <- read.csv(paste0("results/ww_re_estimates", suffix_resp_dist, ".csv"))
# ww_re_scale_sensitivity <- read.csv("results/ww_re_scaling_sensitivity.csv")
# confirmed_case_re <- read.csv("results/confirmed_case_re_estimates.csv")

ww_re <- read.csv("app/data/ww_re_estimates.csv")
confirmed_case_re <- read.csv("app/data/confirmed_case_re_estimates.csv")

# Catchment area data
catchment_area_data <- read.xlsx("proposals/commune_list.xlsx", sheetIndex = 2)

# Wastewater concentration and load data
ww_measurements <- rbind(
  read.csv("data/clean_data_bs.csv"),
  read.csv("data/clean_data_ge_zh.csv")  # summarized raw measurement data
)

# Delay distribution data
fecal_delay_data <- read.csv("data/raw_data/data_for_fecal_shedding_dist.csv")
resp_delay_data <- read.csv("data/raw_data/shedding_profile_carrat_2008.csv")
symptoms_delay_data <- read.csv("data/raw_data/symptoms_score_carrat_2008.csv")
fecal_delay_dist <- read.csv("data/raw_data/shedding_profile_fit_fecal.csv")
resp_delay_dist <- read.csv("data/raw_data/shedding_profile_fit.csv")
symptoms_delay_dist <- read.csv("data/raw_data/symptom_score_fit.csv")
```

Clean catchment area data
```{r}
catchment_area_data <- catchment_area_data %>%
  drop_na(KURZTEXT) %>% # remove all-NA last line
  mutate(commune = recode(KURZTEXT, 
                               "A´re" = "Vernier",
                               "Bruderholz" = "Basel",
                               "Carouge GE" = "Carouge",
                               "ChambÚsy" = "Pregny-Chambésy",
                               "ChÔtelaine" = "Vernier",
                               "ChÛne-Bougeries" = "Chêne-Bougeries",
                               "Cointrin" = "Meyrin",
                               "Collex" = "Collex-Bossy",
                               "Conches" = "Chêne-Bougeries",
                               "GenÞve" = "Genève",
                               "Glattbrugg" = "Opfikon",
                               "Glattpark(Opfikon)" = "Opfikon",
                               "Grand-Lancy" = "Lancy",
                               "Kilchberg ZH" = "Kilchberg",  # TODO: this finds one in Argau
                               "La Croix-de-Rozon" = "Bardonnex",
                               "Le Grand-Saconnex" = "Grand-Saconnex",
                               "Le Lignon" = "Vernier",
                               "Les Acacias" = "Carouge",
                               "Les Avanchets" = "Vernier",
                               "Oberwil BL" = "Oberwil",
                               "Perly" = "Perly-Certoux",
                               "Petit-Lancy" = "Lancy",
                               "R³mlang" = "Rümlang",
                               "Sch÷nenbuch" = "Arlesheim",
                               "Uitikon Waldegg" = "Uitikon",
                               "Vandoeuvres" = "Vandœuvres",
                               "Vessy" = "Veyrier",
                               "VÚsenaz" = "Collonge-Bellerive",
                               "Z³rich" = "Zürich",
                               "Zollikerberg" = "Zollikon"))

catchment_area_summary <- catchment_area_data %>% 
  group_by(ARA_NAMEN, commune) %>%
  summarize(n_plz = n(), per_plz_mean = mean(Per_PLZ), per_plz_sd = sd(Per_PLZ), .groups = "drop") %>%
  mutate(`Wastewater facility` = recode(
    .x = ARA_NAMEN,
    "BASEL" = "Basel (270,000 residents)",
    "VERNIER/AIRE" = "Geneva (445,000 residents)",
    "ZUERICH(WERDHOELZLI)" = "Zurich (670,000 residents)"
  )) %>%
  mutate(district = case_when(commune == "Zürich" ~ "Zürich"))
```

Make map
```{r}
if (remake_map) {
  # Load admin boundaries shapefile
  adm1 <- readOGR(dsn = "./data/spatial_data/gadm41_CHE_shp", layer = "gadm41_CHE_1")  # cantons
  adm3 <- readOGR(dsn = "./data/spatial_data/gadm41_CHE_shp", layer = "gadm41_CHE_3")  # municipalities
  
  # Get municipalities to plot
  data_to_plot <- rbind(
    adm3@data %>%
      filter(NAME_2 != "Zürich") %>%
      left_join(catchment_area_summary, by = c("NAME_3" = "commune")) %>%
      select(-district),
    adm3@data %>%
      filter(NAME_2 == "Zürich") %>%
      left_join(catchment_area_summary, by = c("NAME_2" = "district")) %>%
      select(-commune)
  )
  
  # Fix duplicate commune name (set values to NA for not-meant commune)
  data_to_plot[data_to_plot$NAME_3 == "Kilchberg" & data_to_plot$NAME_2 == "Sissach", 
               c("ARA_NAMEN", "n_plz", "per_plz_mean", "per_plz_sd", "Wastewater facility")] <- NA
  
  # Check no more duplicates
  tmp <- data_to_plot %>% 
    group_by(NAME_3) %>% 
    summarize(n_entries = sum(!is.na(n_plz))) %>% 
    filter(n_entries > 1)
  if (nrow(tmp) > 0) {
    warning("Duplicate commune names remain!")
  }
  
  adm3@data <- data_to_plot
  
  # Set mapping mode to "plot"
  tmap_mode("plot")
  
  # Create base map of one color, then add another shape that is subset to the region of interest
  map_plot <- tm_shape(adm1) + 
      tm_polygons(col = background_plot_color, lwd = 1, alpha = 0.3) + 
    tm_shape(adm3[!is.na(adm3$`Wastewater facility`), ]) +
      tm_polygons("Wastewater facility", palette = catchment_area_colors, lwd = 0) +
    tm_layout(
      frame = FALSE, 
      bg.color = "transparent", 
      legend.title.size = 1,
      legend.text.size =  0.6,
      legend.position = c("right", "bottom")) +
    tm_scale_bar(position = c("left", "bottom"), width = .125)
  
  map_plot
  
  tmap_save(
    map_plot,
    file = "figures/sites_map.tiff",
    device = tiff,
    width = 6,
    height = 4, 
    units = "in",
    bg = "white")
  # tmap_save(map_plot, filename = "figures/sites_map.png", device = png, bg = "transparent")
}
```

Merge Re output data
```{r}
all_re <- rbind(
  ww_re %>% 
    select(-X) %>%
    mutate(data_type = "Wastewater", delay_dist = "Fecal"), 
  # ww_re_resp_dist %>% 
  #   select(-X) %>%
  #   mutate(data_type = "Wastewater", delay_dist = "Respiratory"), 
  confirmed_case_re %>% 
    mutate(data_type = "Cases", delay_dist = "Symptoms") %>% 
    mutate(influenza_type = recode(influenza_type, "A" = "IAV", "B" = "IBV"))
  )
all_re_clean <- all_re %>% 
  mutate(observation_type = recode(
    observation_type,
    "ARA Basel" = "Basel",
    "ARA Werdhölzli" = "Zurich",
    "STEP Aire" = "Geneva",
    "BASEL" = "Basel",
    "ZUERICH(WERDHOELZLI)" = "Zurich",
    "VERNIER/AIRE" = "Geneva",
    "CHUR" = "Chur",
    "BIOGGIO(LUGANO)" = "Lugano",
    "THAL/ALTENRHEIN" = "Altenrhein",
    "LAUPEN(SENSETAL)" = "Laupen")) %>%
  mutate(observation_type = factor(
    observation_type, 
    levels = c("Zurich", "Geneva", "Basel", "Lugano", "Altenrhein", "Laupen", "Chur", "All provided data")))  # decreasing size order
```

Plot Re input data: interpolated, scaled wastewater data and case count data
```{r}
input_data_plot <- ggplot(
  data = all_re_clean %>% filter(delay_dist != "Respiratory"),
  aes(x = as.Date(date), y = observed_incidence, color = influenza_type)) +
  geom_line(size = 0.5) +
  geom_point(size = 0.5) +
  facet_grid(observation_type + measuring_period ~ data_type, scales = "free_y") +
  scale_x_date(date_breaks = "2 months", date_labels = "%b\n%y") +
  influenza_type_color_scale +
  shared_theme + 
  theme(legend.position = "none") +
  labs(x = element_blank(), y = "Incidence")

input_data_plot

ggsave("figures/re_input_data.png", height = 9, width = 8, units = "in")
```

Plot deconvolved incidence estimates
```{r}
estimated_incidence_plot <- ggplot(
  data = all_re_clean %>% 
    filter(!(data_type == "Wastewater" & observation_type == "Basel")) %>%  # remove Basel wastewater estimates because they make the case data scale way too big, uninterpretable
    filter(delay_dist != "Respiratory"),  # use fecal delay dist
  aes(x = as.Date(date), y = deconvolved_incidence, color = influenza_type)) +
  geom_line(size = 0.5) +
  geom_ribbon(
    aes(ymin = CI_down_deconvolved_incidence, ymax = CI_up_deconvolved_incidence, fill = influenza_type),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(observation_type ~ data_type, scales = "free_y") +
  scale_x_date(date_breaks = "2 months", date_labels = "%b\n%y") +
  influenza_type_color_scale +
  shared_theme +
  theme(legend.position = "none") +
  labs(x = element_blank(), y = "Deconvolved incidence")

estimated_incidence_plot

ggsave(filename = "figures/deconvolved_incidence.png", height = 9, width = 8, units = "in")
```

Plot Re estimates
```{r}
estimated_re_plot <- ggplot(
  data = all_re_clean %>% filter(delay_dist != "Respiratory"), 
  aes(x = as.Date(date), y = Re_estimate, color = influenza_type)) +
  geom_hline(aes(yintercept = 1), linetype = "solid", color = "darkgray") +
  geom_line(size = 0.5) +
  geom_ribbon(
    aes(ymin = CI_down_Re_estimate, ymax = CI_up_Re_estimate, fill = influenza_type),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(observation_type ~ data_type, scales = "free_y") +
  scale_x_date(date_breaks = "2 months", date_labels = "%b\n%y") +
  influenza_type_color_scale +
  shared_theme +
  theme(legend.position = "none") +
  labs(x = element_blank(), y = "Reproductive number") +
  scale_y_continuous(limits = c(0, 2.5), oob = oob_squish, breaks = c(0, 1, 2))

estimated_re_plot

ggsave(filename = "figures/re_all.png", height = 9, width = 8, units = "in")
```

Get data to plot in main text
```{r}
measurement_data_to_plot <- ww_measurements %>%
  filter(measurement_type %in% c("IAV_gc_per_day", "IBV_gc_per_day")) %>%
  mutate(influenza_type = recode(
    measurement_type,
    "IAV_gc_per_day" = "IAV",
    "IBV_gc_per_day" = "IBV",
  )) %>%
  mutate(observation_type = recode(
    wwtp,
    "ARA Basel" = "Basel",
    "STEP Aire" = "Geneva",
    "ARA Werdhölzli" = "Zurich"
  )) %>%
  filter(sample_date >= as.Date("2021-12-01"), sample_date < as.Date("2022-05-01")) %>%
  mutate(observation_type = factor(observation_type, levels = catchment_factor_levels))

re_data_to_plot <- all_re_clean %>%
  filter(observation_type %in% c("Zurich", "Geneva", "All provided data")) %>%
  filter(date >= as.Date("2021-12-01"), date < as.Date("2022-05-01")) %>%
  filter(delay_dist != "Respiratory") %>%
  mutate(observation_type = factor(observation_type, levels = catchment_factor_levels))

highlight_data <- data.frame(
  re_threshold = 1,
  influenza_type = c("IAV", "IAV", "IAV", "IAV", "IBV", "IBV", "IBV", "IBV"),
  observation_type = rep(c("Geneva", "Zurich"), 4),
  data_type = c("Cases", "Cases", "Wastewater", "Wastewater", "Cases", "Cases", "Wastewater", "Wastewater")
) %>%
  filter(!(influenza_type == "IBV" & data_type == "Cases")) %>%  # remove highlight for panels without Re
  mutate(observation_type = factor(observation_type, levels = catchment_factor_levels))
```

Make main text figure for wastewater ww_measurements
```{r}
ggplot(
  data = measurement_data_to_plot %>% filter(mean > 0),
  aes(x = as.Date(sample_date), y = mean, color = "Wastewater")) + 
  geom_point(size = 0.5) +
  geom_point(data = measurement_data_to_plot %>% filter(mean == 0), size = 0.5, shape = 4) +
  geom_errorbar(
    data = measurement_data_to_plot %>% filter(mean > 0, n_measurements > 1),
    aes(ymin = min, ymax = max), 
    size = 0.5, width = 5) +
  facet_grid(influenza_type ~ observation_type) +
  shared_theme + 
  shared_date_scale_coarse +
  data_type_color_scale +
  theme(legend.position = "none") +
  labs(x = element_blank(), y = "Genome copies per day")

ggsave("figures/ww_data_focus.png", width = 6.5, height = 4, units = "in")
```

Make main text figure comparing case- and wasetwater-based estimates around the time of Omicron measures
```{r}
ggplot(data = re_data_to_plot) +
  geom_rect(
    data = highlight_data %>% filter(data_type == "Wastewater"),
    aes(
      ymin = -Inf, ymax = Inf, 
      xmin = as.Date("2021-12-06"), xmax = as.Date("2022-02-16")),  # work from home reccommendation
    alpha = 0.15) +
  geom_rect(
    data = highlight_data %>% filter(data_type == "Wastewater"),  # prevent double-plotting
    aes(
      ymin = -Inf, ymax = Inf, 
      xmin = as.Date("2021-12-20"), xmax = as.Date("2022-02-03")),  # work from home mandate
    alpha = 0.15) +
  geom_line(aes(x = as.Date(date), y = deconvolved_incidence, color = data_type), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date),
      ymin = CI_down_deconvolved_incidence, ymax = CI_up_deconvolved_incidence,
      fill = data_type),
    alpha = 0.2) +
  facet_grid(influenza_type ~ observation_type) +
  data_type_color_scale +
  shared_theme +
  theme(legend.position = "bottom") +
  shared_date_scale +
  labs(x = element_blank(), y = "Deconvolved incidence")

ggsave("figures/deconvolved_incidence_comparision_focus.png", width = 6.5, height = 4, units = "in")
```

Make main text figure comparing case- and wasetwater-based estimates around the time of Omicron measures
```{r}
ggplot(data = re_data_to_plot) +
  geom_hline(data = highlight_data, aes(yintercept = re_threshold), color = "darkgray") +
  geom_rect(
    data = highlight_data %>% filter(data_type == "Wastewater"),
    aes(
      ymin = -Inf, ymax = Inf, 
      xmin = as.Date("2021-12-06"), xmax = as.Date("2022-02-16")),  # work from home reccommendation
    alpha = 0.15) +
  geom_rect(
    data = highlight_data %>% filter(data_type == "Wastewater"),  # prevent double-plotting
    aes(
      ymin = -Inf, ymax = Inf, 
      xmin = as.Date("2021-12-20"), xmax = as.Date("2022-02-03")),  # work from home mandate
    alpha = 0.15) +
  geom_line(aes(x = as.Date(date), y = Re_estimate, color = data_type), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date), y = Re_estimate,
      ymin = CI_down_Re_estimate, ymax = CI_up_Re_estimate,
      fill = data_type),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(influenza_type ~ observation_type) +
  data_type_color_scale +
  shared_theme +
  theme(legend.position = "bottom") + 
  shared_date_scale +
  labs(x = element_blank(), y = "Reproductive number") +
  scale_y_continuous(limits = c(0, 3), oob = oob_squish, breaks = c(0, 1, 2, 3))

ggsave("figures/re_comparision_focus.png", width = 6.5, height = 4, units = "in")
```

Basel incidence and Re estimates for supplement
```{r}
basel_re_data_to_plot <- all_re_clean %>%
  filter(observation_type == c("Basel"), data_type == "Wastewater", influenza_type == "IAV") %>%
  filter(delay_dist != "Respiratory") %>%
  filter(date >= as.Date("2021-12-01"), date < as.Date("2022-05-01"))

basel_incidence_plot <- ggplot(data = basel_re_data_to_plot) +
  geom_line(aes(x = as.Date(date), y = deconvolved_incidence, color = data_type), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date),
      ymin = CI_down_deconvolved_incidence, ymax = CI_up_deconvolved_incidence,
      fill = data_type),
    alpha = 0.2) +
  facet_grid(influenza_type ~ observation_type) +
  data_type_color_scale +
  shared_theme +
  theme(legend.position = "none") +
  shared_date_scale +
  labs(x = element_blank(), y = "Deconvolved incidence")

basel_re_plot <- ggplot(data = basel_re_data_to_plot) +
  geom_hline(aes(yintercept = 1), color = "darkgray") +
  geom_line(aes(x = as.Date(date), y = Re_estimate, color = data_type), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date), y = Re_estimate,
      ymin = CI_down_Re_estimate, ymax = CI_up_Re_estimate,
      fill = data_type),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(influenza_type ~ observation_type) +
  data_type_color_scale +
  shared_theme +
  theme(legend.position = "none") +
  shared_date_scale +
  labs(x = element_blank(), y = "Reproductive number") +
  scale_y_continuous(limits = c(0, 3), oob = oob_squish, breaks = c(0, 1, 2, 3))

cowplot::plot_grid(basel_incidence_plot, basel_re_plot, labels = c('A', 'B'), nrow = 2, align = "v")

ggsave("figures/basel_incidence_re.png", width = 4, height = 5, units = "in")
```

Plot various delay distributions for supplement
```{r}
fecal_delay_plot <- ggplot(
    data = fecal_delay_data %>% filter(measurement < 4E6),  # filter outlier for plotting only, was used for fitting
    aes(x = measurement.day, y = measurement)) + 
    geom_point(aes(shape = "Empirical data")) +
    geom_line(
        data = data.frame(measurement.day = seq(to = 35, by = 0.5)) %>% 
            mutate(measurement = fecal_delay_dist$empirical_dist_integral * dgamma(
              x = measurement.day, shape = fecal_delay_dist$shape, scale = fecal_delay_dist$scale)),
        aes(linetype = "Gamma fit")) + 
    theme_bw() +
    theme(legend.position = "bottom", legend.title = element_blank(), legend.spacing.x = unit(0.1, 'cm')) +
    labs(x = "Days after symptom onset + 2", y = "Genome copies\nper gram feces")

resp_delay_plot <- ggplot(
    data = resp_delay_data %>% mutate(viral_titer = 10^log_viral_titer),
    aes(x = days_after_innoculation, y = viral_titer)) + 
    geom_point(aes(shape = "Carrat 2008 data")) +
    geom_line(
        data = data.frame(days_after_innoculation = seq(from = 0, to = 10, by = 0.1)) %>% 
            mutate(viral_titer = resp_delay_dist$empirical_dist_integral[2] * dgamma(
              x = days_after_innoculation, shape = resp_delay_dist$shape[2], scale = resp_delay_dist$scale[2])),
        aes(linetype = "Gamma fit")) +
    labs(x = "Days after innoculation", y = "Viral RNA\nin respiratory sample") +
    theme_bw() +
    scale_x_continuous(breaks = seq(0, 10, 1)) +
    scale_y_continuous(limits = c(0, NA), oob = scales::oob_keep) +
    theme(legend.position = "bottom", legend.title = element_blank(), legend.spacing.x = unit(0.1, 'cm'))

symptom_delay_plot <- ggplot(
    data = symptoms_delay_data,
    aes(x = days_after_innoculation, y = symptom_score)) + 
    geom_point(aes(shape = "Carrat 2008 data")) +
    geom_line(
        data = data.frame(days_after_innoculation = seq(from = 0, to = 10, by = 0.1)) %>% 
            mutate(symptom_score = symptoms_delay_dist$empirical_dist_integral * dgamma(
              x = days_after_innoculation, shape = symptoms_delay_dist$shape, scale = symptoms_delay_dist$scale)),
        aes(linetype = "Gamma fit")) +
    labs(x = "Days after innoculation", y = "Symptoms score") +
    theme_bw() +
    scale_x_continuous(breaks = seq(0, 10, 1)) +
    scale_y_continuous(limits = c(0, NA), oob = scales::oob_keep) +
    theme(legend.position = "bottom", legend.title = element_blank(), legend.spacing.x = unit(0.1, 'cm'))

cowplot::plot_grid(
  symptom_delay_plot,
  fecal_delay_plot,
  resp_delay_plot,
  align = "hv",
  labels = c("A", "B", "C"))

ggsave("figures/delay_distributions.png", width = 6.5, height = 5.5, units = "in")
```

Plot sensitivity analysis with respiratory delay distribution for supplement
```{r}
delay_dist_incidence_plot <- ggplot(
  data = all_re_clean %>% 
    filter(data_type == "Wastewater", observation_type != "Basel")) +
  geom_hline(aes(yintercept = 1), color = "darkgray") +
  geom_line(aes(x = as.Date(date), y = deconvolved_incidence, color = delay_dist), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date), y = deconvolved_incidence,
      ymin = CI_down_deconvolved_incidence, ymax = CI_up_deconvolved_incidence,
      fill = delay_dist),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(influenza_type ~ observation_type) +
  delay_dist_color_scale +
  shared_theme +
  theme(legend.position = "none") +
  shared_date_scale +
  labs(x = element_blank(), y = "Deconvolved incidence")

delay_dist_re_plot <- ggplot(
  data = all_re_clean %>% 
    filter(data_type == "Wastewater", observation_type != "Basel")) +
  geom_hline(aes(yintercept = 1), color = "darkgray") +
  geom_line(aes(x = as.Date(date), y = Re_estimate, color = delay_dist), size = 0.5) +
  geom_ribbon(
    aes(
      x = as.Date(date), y = Re_estimate,
      ymin = CI_down_Re_estimate, ymax = CI_up_Re_estimate,
      fill = delay_dist),
    alpha = 0.3,
    linetype = 0) +
  facet_grid(influenza_type ~ observation_type) +
  delay_dist_color_scale +
  shared_theme +
  theme(legend.position = "bottom") +
  shared_date_scale +
  labs(x = element_blank(), y = "Reproductive number") +
  scale_y_continuous(limits = c(0, 3), oob = oob_squish, breaks = c(0, 1, 2, 3))

cowplot::plot_grid(delay_dist_incidence_plot, delay_dist_re_plot, labels = c('A', 'B'), nrow = 2, align = "vh", axis = "tblr")

ggsave("figures/delay_dist_incidence_re.png", width = 6.5, height = 6, units = "in")
```

Plot sensitivity analysis for wastewater measurement scaling for supplement
```{r}
ggplot(
    data = ww_re_scale_sensitivity,
    aes(x = as.Date(date), y = Re_estimate, color = influenza_type, fill = influenza_type)
) + facet_grid(scaling_type ~ influenza_type, labeller = label_wrap_gen(width = 20)) +
    geom_line() +
    geom_ribbon(aes(ymax = CI_up_Re_estimate, ymin = CI_down_Re_estimate), alpha = 0.45, colour = NA) +
    influenza_type_color_scale +
    shared_theme +
    theme(legend.position = "none") +
    shared_date_scale +
    labs(x = element_blank(), y = "Reproductive number") +
    scale_y_continuous(limits = c(0, 3), oob = oob_squish, breaks = c(0, 1, 2, 3))

ggsave("figures/sensitivity_analysis_scaling.png", width = 6.5, height = 6, units = "in")
```

Get statistics for for paper
```{r}
ww_measurements_load <- ww_measurements %>%
  filter(endsWith(x = measurement_type, suffix = "gc_per_day")) %>%
  filter(sample_date >= as.Date("2021-12-01"), sample_date < as.Date("2022-05-01"))

# Number of days per week sampled
ww_measurements_load %>%
  mutate(week = format(as.Date(sample_date), "%Y-%V")) %>%
  group_by(wwtp, measurement_type, week) %>%
  summarize(n_samples_per_week = n(), .groups = "drop") %>%
  group_by(wwtp, measurement_type) %>%
  summarize(avg_n_samples_per_week = mean(n_samples_per_week), n_weeks = n())

# Number of replicates
ww_measurements_load %>%
  group_by(wwtp, measurement_type) %>%
  summarize(mean_n_replicates = mean(n_measurements))

# Number of days when IAV and IBV detected
ww_measurements_load %>%
  group_by(wwtp, measurement_type) %>%
  summarize(n_samples = n(), n_detect = sum(mean != 0), n_non_detect = sum(mean == 0)) %>%
  mutate(frac_non_detect = n_non_detect / n_samples)

# IAV and IBV confirmed cases
re_data_to_plot %>%
  filter(data_type == "Cases") %>%
  group_by(observation_type, influenza_type) %>%
  summarize(n_observations = sum(observed_incidence))
all_re_clean %>%
  filter(observation_type == c("Basel"), data_type == "Cases") %>%
  filter(delay_dist != "Respiratory") %>%
  filter(date >= as.Date("2021-12-01"), date < as.Date("2022-05-01")) %>%
  filter(data_type == "Cases") %>%
  group_by(observation_type, influenza_type) %>%
  summarize(n_observations = sum(observed_incidence))

# Time shift based on respiratory distribution
all_re_clean %>%
  group_by(observation_type, data_type, influenza_type, delay_dist) %>%
  filter(deconvolved_incidence == max(deconvolved_incidence, na.rm = T)) %>%
  select(observation_type, data_type, influenza_type, delay_dist, date, deconvolved_incidence)

# Cumulative estimated infection incidence
re_data_to_plot %>%
  group_by(observation_type, data_type, influenza_type) %>%
  summarise(
    deconvolved_incidence_total = sum(deconvolved_incidence, na.rm = T),
    CI_down_deconvolved_incidence_total = sum(CI_down_deconvolved_incidence, na.rm = T),
    CI_up_deconvolved_incidence_total = sum(CI_up_deconvolved_incidence, na.rm = T),
    min_date = min(date), max_date = max(date))
```